Super vs fficient absorption of light by spherical nanoparticles

### 2015-07-06 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-aem.tex
merge of Andrey changes

\begin{abstract}
  Nanoparticles have a fundamental limit as to
  how much light they can absorb. This limit is based on the
  finite number of modes excited inside the nanoparticle at a given wavelength and maximal absorption capacity per mode. Thus, the enhanced absorption can be achieved when each mode supported by the nanopartice absorbs light up to the maximal capacity. Using genetic algorithm, we design multi-layer nanoparticles, in which we
  can make several resonant modes overlap at the same frequency resulting in {\it super-absorption}. 
  We further introduce the {\it efficiency of
  the absorption} for a nanoparticle, which is absorption normalized by
  the physical size of the particle, and show that efficient absorbers
  are not always operating in super-absorbing regime.
\end{abstract}

@@

Mie theory~\cite{Mie-1908}, which is over 100 years old now, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great current interest~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
study the multilayered spherical
particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
various applications in cancer treatment~\cite{Zhang-2010,
  Hirsch-2003} and medical diagnostics~\cite{Allain-2002},
cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic~\cite{Martin-2013, Alu-2005} devices, study on thermal
properties of insulating material~\cite{Xie-2013}, as well as for
improving solar cells performance~\cite{Kameya-2011,Mann-2011}, and so
on.

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In these
works authors introduced the concept of a super-scattering, when the
scattering cross-section of a multilayer particle exceeds that of a
homogeneous particle of the same size in the so-called single-channel
limit. The super scattering appears when we design a multilayer
structure so that several modes become nearly degenerate, i.e. their
resonance frequencies coincide or get close to each other. In a
homogeneous particle, the resonances appear at different frequencies,
and there is no design freedom for a fixed geometry of the structure
to make these resonances overlap, and this limits the achievable
scattering cross-section.

@@

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of the optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved at the particle radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. Second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at R=63~nm and R=81~nm. (b) Mie absorption
      coefficients for individual excited modes of the optimized
      structures. (c) Optimized layer thicknesses. For the total
      particle radius below 46~nm the optimizer converges to
      the two-layer structure, when core size vanishes, and the
      optimum design is a bi-layer $Ag/Si$ particle.

      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency.  We show the results of our genetic optimization algorithm
in Fig.~\ref{fig:overview}a.  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm abs\
  max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi R_{\rm
  total}/\lambda$, and $n$ is an angular momentum of the
mode. Following Ref.~\cite{Fan-2011}, where authors introduced a super
scattering for spherical particles, here we introduce
super-absorption. In our parameter space we have just modes up to the quadrupole
excited ($n=2$), and in order to get a super-absorption our efficiency
should be higher than that of a quadrupole. We clearly see this
super-absorption at $R_{\rm total}>60$~nm, in Fig.~\ref{fig:overview}
(a).

>>>>

\begin{abstract}
  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited
  inside the nanoparticle at a given wavelength and maximal absorption
  capacity per mode. Thus, the enhanced absorption can be achieved
  when each mode supported by the nanopartice absorbs light up to the
  maximal capacity. Using stochastic optimization algorithm, we design
  multi-layer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in {\it
    super-absorption}.  We further introduce the {\it efficiency of
    the absorption} for a nanoparticle, which is absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in super-absorbing regime.
\end{abstract}

@@

Mie theory~\cite{Mie-1908}, which is over 100 years old now, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great current
interest~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
study the multilayered spherical
particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
various applications in cancer treatment~\cite{Zhang-2010,
  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic~\cite{Martin-2013, Alu-2005} devices, study on thermal
properties of insulating material~\cite{Xie-2013}, as well as for
improving solar cells performance~\cite{Kameya-2011,Mann-2011}, and so
on.

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In
these works authors introduced the concept of a super-scattering, when
the scattering cross-section of a multilayer particle exceeds that of
a homogeneous particle of the same size in the so-called
single-channel limit. The super-scattering appears when we design a
multilayer structure so that several modes become nearly degenerate,
i.e. their resonance frequencies coincide or get close to each
other. In a homogeneous particle, the resonances appear at different
frequencies, and there is no design freedom for a fixed geometry of
the structure to make these resonances overlap, and this limits the
achievable scattering cross-section.

@@

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of the optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved at the particle radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. Second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at $R=63$~nm and $R=81$~nm. TODO add arrows to mark
      local maxima on the plot (b) Mie absorption
      coefficients for individual excited modes of the optimized
      structures. (c) Optimized layer thicknesses. For the total
      particle radius below 46~nm the optimizer converges to
      the two-layer structure, when core size vanishes, and the
      optimum design is a bi-layer $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency.  We show the results of our genetic optimization algorithm
in Fig.~\ref{fig:overview}a.  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
R_{\rm total}/\lambda$, and $n$ is an angular momentum of the
mode. Following Ref.~\cite{Fan-2011}, where authors introduced a super
scattering for spherical particles, here we introduce
super-absorption. In our parameter space we have just modes up to the
quadrupole excited ($n=2$), and in order to get a super-absorption our
efficiency should be higher than that of a quadrupole. We clearly see
this super-absorption at $R_{\rm total}>60$~nm, in
Fig.~\ref{fig:overview} (a).
